\subsection{Operation Model for oeCreateNewCrisisEvent}

\label{OM-oeCreateNewCrisisEvent}


The \msrcode{oeCreateNewCrisisEvent} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeCreateNewCrisisEvent}{sent to create a new crisis event and to alert the corresponding coordinators.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{AName: dtString}{the name of the notifier that informed the Central Coordinator of the crisis event.} 
	\addnumbereddoublerow{}{AetHumanType: etHumanType}{the notifier can be either a victim or a witness.} 
	\addnumbereddoublerow{}{AdtPhoneNumber: dtPhoneNumber}{the phone number of the notifier.} 
	\addnumbereddoublerow{}{AdtMapWithPin: dtMapWithPin}{a map with pin showing the crisis event's location.} 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{The actor's mode is \msrcode{isInAddEvent}.}
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{The map with pin provided by the central coordinator only has a single pin. }

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{A new crisis event is created and initialised with
		a new crisis event id attribute which is the \msrcode{nextValueForAlertID}@pre in \msrcode{ctState}
		and the geographical position attribute of the crisis event which is extracted from the map with pin provided by the central coordinator.}
	\addnumberedsinglerow{PostF}{An alert message 'You have received a new dispatch order!' together with new crisis event id is sent to a free FiremenCoordinator and a free TowServiceCoordinator that are geographically the nearest of the crisis event's
	 location and their dispatch status attributes are set to 'InStation'.}
	\addnumberedsinglerow{PostF}{The new crisis event is then associated to :\newline
		the central coordinator who created this instance,\newline
		the two selected dispatch coordinators,\newline
		the map with pin instance that has the map with pin attriubute communicated by the central central coordinator in the parameters,\newline
		the human instance, who may be initialised, if he/she is not yet in the system state, with his/her phone number as the unique id, a name and a type (witness/victim) which are given as parameters by the central coordinator,\newline
		comment instance(s) which is/are initalised if the central coordinator has given some additional comments to the crisis event.
	}
	\addnumberedsinglerow{PostF}{The two selected dispatch coordinators' attribute\msrcode{isFree} is set to false and can thus no more be associated to another crisis event.}
	\addnumberedsinglerow{PostF}{the attribute\msrcode{nextValueForAltertID} in ctState instance should be equal to the one @pre incremented by one.}

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{The actor's mode is set to \msrcode{isInMain}.}
	\addnumberedsinglerow{PostP}{the two selected dispatch coordinators' modes are set to \msrcode{hasBeenAssociatedToACrisisEvent}.}
	\addnumberedsinglerow{PostP}{the selected firemen coordinator's modeFM is set to \msrcode{isNotInRequestHelp}.}
	\end{operationmodel}



	
	
	
	





