% Last Modification:
% @author AUTHOR_NAME
% @date TODAY_DATE

\chapter{General Description}
\label{chap:general_description}


\section{Domain Stakeholders}
\label{sec:icrash-gendescr-stakeholders}
All stakeholders of the system are detailed in this section. After a brief description of a
stakeholder, its objectives are first stated. Thereafter, the responsibilities of
the stakeholder are detailed which help to achieve the stakeholder objectives to a certain
degree. While the objectives characterize the general problems addressed by the \msricrashmini system,
the responsibilities describe concrete actions that are expected from a stakeholder. Some of
these responsibilities can be traced looking at the use case described in
Section 2.3, and hence must be supported by the \msricrashmini  system. 
All stakeholders listed in this section have an interest in the system or are affected
by the system in some way, but only a subset of the stakeholders are directly involved in the use
cases described.
Let us remind that use case diagrams or descriptions are not \msrmessir analysis phase mandatory outputs. They are proposed as informal means to help understanding the semantics of the system specification made of the mandatory analysis models, which provide a complete executable specification.

\newpage

\section{System's Actors}
\label{sec:icrash-gendescr-actors}
\subsection{Emergency Central}
\subparagraph{Emergency Central Administrator}
Most likely a chief or someone with high autorities in the Emergency Central. His
job is to assign fellow colleagues as coordinators.

\subparagraph{Emergency Central Coordinator}
An Emergency Central Coordinator is an employee who has been given special rights
by the administrator. His job is:

\begin{enumerate}
\item To check the incident's location with the notifier.
\item To create the new event in the system.
\item To send a dispatch message to the corresponding coordinators.
\end{enumerate}


\subsection{Firemen}
General idea : The most important dispatched coordinators, because they are the
ones sitting in the ambulances and providing first aids to the injured individuals.

\subparagraph{Firemen Administrator}
Most likely a chief or someone with high autorities in the Firemen Department.
His job is to assign fellow colleagues as coordinators.

\subparagraph{Firemen Coordinator}
A Firemen Coordinator is a Team Leader who has been given special
rights by the administrator. His job is:

\begin{enumerate}
\item To assemble his team as soon as possible when a dispatch request is
received.
\item To provide information on his Team's whereabouts.
\item To call for backup if needed when on-site.
\item To send messages if needed.
\end{enumerate}

\subsection{Tow Service}
General idea : Dispatched coordinators responsible of clearing the highway of
the destroyed cars.

\subparagraph{Tow Service Administrator}
Most likely a chief or someone with high autorities in the Tow Service.
His job is to assign fellow colleagues as coordinators.

\subparagraph{Tow Service Coordinator}
A Tow Service Coordinator is a Team Leader who has been given special
rights by the administrator. His job is:

\begin{enumerate}
\item To assemble his team as soon as possible when a dispatch request is
received.
\item To provide information on his Team's whereabouts.
\item To send messages if needed.
\end{enumerate}

\subsection{Police}
General idea : General idea : Dispatched coordinators responsible of solving
eventual conflicts between the victims.

\subparagraph{Police Administrator}
Most likely a chief or someone with high autorities in the Police Department.
His job is to assign fellow colleagues as coordinators.

\subparagraph{Police Coordinator}
A Police Coordinator is a Team Leader who has been given special
rights by the administrator. His job is:

\begin{enumerate}
\item To assemble his team as soon as possible when a dispatch request is
received.
\item To provide information on his Team's whereabouts.
\item To send messages if needed.
\end{enumerate}


\subsection{Communication Company}
A Communication Company is a company who provides fixed and mobile voice
services like POST, TANGO, ORANGE, etc. Its job is to transfer any emergency
calls to the Emergency Central and to provide the notifier's
geographical postion via its network to the system.

\newpage
