\subsection{Primary types - Class types descriptions}




The table below is providing comments on the graphical views given for the class types of the primary types. Type logical operations are precisely specified in the operation model.

\begin{datadictionary}
\addheading{Classes}

\adddoublerow{ctComment}{A class containing a comment.}
\adddoubletwocolumnrow{attribute}{\msrcode{comment: dtComment}}{}
\adddoubletwocolumnrow{operation}{\msrcode{init(AComment:dtComment):ptBoolean}}{}
\adddoublerow{ctCrisisEvent}{A class containing the attributes identifying a crisis event.}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtCrisisID}}{}
\adddoubletwocolumnrow{attribute}{\msrcode{isLocationConfirmed: ptBoolean}}{}
\adddoubletwocolumnrow{attribute}{\msrcode{location: dtMapWithPin}}{}
\adddoubletwocolumnrow{operation}{\msrcode{init(Aid:dtCrisisID, Alocation:dtMapWithPin, AisLocationConfirmed:ptBoolean, Acomment:ptString, AgeoPos:dtGeoPos):ptBoolean}}{}
\adddoublerow{ctDispatchedCoordinator}{A class containing the attributes identifying a dispatched team.}
\adddoubletwocolumnrow{attribute}{\msrcode{status: etDispatchStatus}}{}
\adddoubletwocolumnrow{attribute}{\msrcode{type: etTeamType}}{}
\adddoubletwocolumnrow{operation}{\msrcode{init(Atype:etTeamType, Astatus:etDispatchStatus, AgeoPos:dtGeoPos):ptBoolean}}{}
\adddoublerow{ctHuman}{A class containing the attributes identifying an human.}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtPhoneNumber}}{}
\adddoubletwocolumnrow{attribute}{\msrcode{name: ptString}}{}
\adddoubletwocolumnrow{attribute}{\msrcode{type: etHumanType}}{}
\adddoubletwocolumnrow{operation}{\msrcode{init(Aid:dtPhoneNumber, Aname:ptString, Atype:etHumanType):ptBoolean}}{}
\adddoublerow{ctMapWithPin}{A class containing an image which is the map including the pins.}
\adddoubletwocolumnrow{attribute}{\msrcode{mapWithPin: dtMapWithPin}}{}
\adddoubletwocolumnrow{operation}{\msrcode{init(AmapWithPin:dtMapWithPin):ptBoolean}}{}
\adddoublerow{ctState}{used to model the system.}
\adddoubletwocolumnrow{attribute}{\msrcode{vpStarted: ptBoolean}}{}
\adddoubletwocolumnrow{operation}{\msrcode{init(ANextValueForAlertID:ptInteger, AvpStarted:ptBoolean):ptBoolean}}{}
\end{datadictionary}
