\subsection{Primary types - Datatypes types descriptions}





The table below is providing comments on the graphical views given for the datatype types of the primary types.


\begin{datadictionary}
\addheading{Datatypes}

\adddoublerow{dtGeoPos}{Two Real numbers used to identify a geographical position on earth.}
\adddoubletwocolumnrow{attribute}{\msrcode{latitude: dtLatitude}}{}
\adddoubletwocolumnrow{attribute}{\msrcode{longitude: dtLongitude}}{}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{}
\adddoublerow{dtInteger}{A primary type Integer incuding some basic Integer operations.}
\adddoubletwocolumnrow{attribute}{\msrcode{value: ptInteger}}{}
\adddoublerow{dtReal}{A primary type Real incuding some basic Real operations.}
\adddoubletwocolumnrow{attribute}{\msrcode{value: ptReal}}{}
\adddoublerow{dtString}{A primary type String incuding some basic String operations.}
\adddoubletwocolumnrow{attribute}{\msrcode{value: ptString}}{}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{}
\adddoubletwocolumnrow{operation}{\msrcode{length():ptInteger}}{}
\adddoubletwocolumnrow{operation}{\msrcode{myStringConcat(AdtString2IN:dtString):dtString}}{}
\end{datadictionary}


\begin{datadictionary}
\addheading{Enumerations}

\adddoublerow{etDispatchStatus}{A String used to identify a dispatch status.}
\adddoublerow{etHumanType}{A String used to identify an Human type.}
\adddoublerow{etTeamType}{A String used to identify a team type.}
\end{datadictionary}





