\subsubsection{subfunction-oeCreateNewCrisisEvent}

\label{RE-use-case-oeCreateNewCrisisEvent}


sent to create a new crisis event and to alert the corresponding coordinators.		  


\begin{usecase}
  \addheading{Use-Case Description}
  \addsingletwocolumnrow{Name}{oeCreateNewCrisisEvent}
  \addsingletwocolumnrow{Scope}{system}
  \addsingletwocolumnrow{Level}{subfunction}
  
\addrowheading{Parameters}
\addnumberedsinglerow{AdtName: ptString}{used to initialise the name field.}
\addnumberedsinglerow{AetHumanType: etHumanType}{used to initialise the type field.}
\addnumberedsinglerow{AdtPhoneNumber: dtPhoneNumber}{used to initialise the phone number field.}
\addnumberedsinglerow{AdtMapWithPin: dtMapWithPin}{used to initialise the map with pins field.}

\addrowheading{Primary actor(s)}
\addnumberedsinglerow{}{\msrcode{actCentralCoordinator[active]}}


\addrowheading{Secondary actor(s)}
\addnumberedsinglerow{}{\msrcode{actAbstractDispatchCoordinator[passive]}}

\addrowheading{Goal(s) description}
\addsinglerow{sent to create a new crisis event and to alert the corresponding coordinators.}

\addrowheading{Protocol condition(s)}
\addnumberedsinglerow{}{
none.}

\addrowheading{Pre-condition(s)}
\addnumberedsinglerow{}{
the boolean \msrcode{isLocationConfirmed} of this crisis event is set to true.}

\addrowheading{Main post-condition(s)}
\addnumberedsinglerow{}{
a dispatch order including the crisis event's information such as the id, map with pins, witness's phone number, etc. is sent to nearest, free Firemen Team and Tow Service Team.}

\addrowheading{Additional Information}
\addsinglerow{
none
}

\end{usecase} 

